\documentclass{beamer}

\usetheme{Warsaw}

\title{Dist::Zilla - Distribution Swiss Army Knife}
\author{Rob Hoelz}
\institute{INOC}
\date{September 20th, 2011}

\usepackage{ulem}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
Before we begin, I'd like a show of hands...
\end{frame}

\begin{frame}
How many of you have written a Perl module?
\end{frame}

\begin{frame}
How many of you have released one to the CPAN?
\end{frame}

\begin{frame}
For those of you who didn't raise your hands...
\pause
Why not?
\end{frame}

\begin{frame}
I learned Perl in 2006, and yet I didn't release my first module to the CPAN until this past January
\end{frame}

\begin{frame}
Why Not?
\end{frame}

\begin{frame}
Fear is the mind killer!
\end{frame}

\begin{frame}
Fear is the \sout{mind} module killer!
\end{frame}

\begin{frame}
I was afraid I'd screw something up!
\end{frame}

\begin{frame}
Truth is, there's a lot that goes into releasing a module!
\end{frame}

\begin{frame}

\begin{center}
\LARGE{Namely...}
\end{center}

\begin{itemize}
\pause \item \large{Writing (good) tests. (you \textit{are} writing tests, right?}
\pause \item \large{Writing code that passes those tests.}
\pause \item \large{Maintaining your Changes file.}
\pause \item \large{Maintaining your README file.}
\pause \item \large{Maintaining your LICENSE file.}
\pause \item \large{Maintaining your MANIFEST file.}
\pause \item \large{Maintaining your documentation.}
\pause \item \large{Maintaining your Makefile.PL/Build.PL.}
\pause \item \large{Maintaining your META.yml/META.json.}
\pause \item \large{Making sure all of your versions match.}
\end{itemize}

\pause

\large{And you have to remember to do all of these things for every single release of every distribution you write.}
\end{frame}

\begin{frame}
\large{To quote the ShipIt distribution...} \\
\pause
\large{\textit{"This is all a pain in the ass."}}
\end{frame}

\end{document}
