\begin{frame}
\titlepage
\end{frame}

\begin{frame}
Before we begin, I'd like a show of hands...
\end{frame}

\begin{frame}
How many of you have written a Perl module?
\end{frame}

\begin{frame}
How many of you have released one to the CPAN?
\end{frame}

\begin{frame}
For those of you who didn't raise your hands for the second question but raised them for the first...
\pause
Why not?
\end{frame}

\begin{frame}
I learned Perl in 2006, and yet I didn't release my first module to the CPAN until this past January.
\end{frame}

\begin{frame}
Why not?
\end{frame}

\begin{frame}
Fear is the mind killer!
\end{frame}

\begin{frame}
Fear is the \sout{mind} module killer!
\end{frame}

\begin{frame}
I was afraid I'd screw something up!
\end{frame}

\begin{frame}
Truth is, there's a lot that goes into releasing a module!
\end{frame}

\begin{frame}

\begin{center}
\LARGE{Namely...}
\end{center}

\begin{itemize}
\pause \item Writing (good) tests. (you \textit{are} writing tests, right?)
\pause \item Writing code that passes those tests.
\pause \item Maintaining your Changes file.
\pause \item Maintaining your README file.
\pause \item Maintaining your LICENSE file.
\pause \item Maintaining your MANIFEST file.
\pause \item Maintaining your documentation.
\pause \item Maintaining your Makefile.PL/Build.PL.
\pause \item Maintaining your META.yml/META.json.
\pause \item Making sure all of your versions match.
\end{itemize}

\pause

And you have to remember to do all of these things for every single release of every distribution you write.
\end{frame}

\begin{frame}
To quote the ShipIt distribution... \\
\pause
\textit{"This is all a pain in the ass."}
\end{frame}

\begin{frame}
This is how I released my first few modules. \\
\pause
Don't do this. \\
\pause
Use... \pause Dist::Zilla!
\end{frame}
